Automated verification of stand-alone solar photovoltaic systems

### 2018-11-20 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

The flowchart of the proposed automated verification tool is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
As Step 1, the PV input data (e.g., load power demand and load consumption of energy), the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In Step 2, occurs the sizing check of the PV system to make sure that the components accepted international requirements toward a well designed PV project.

@@

The weather variables (solar irradiance and ambient temperature by default) will be explored in all their states by the ESBMC verification engine, in Step 3, based on maximum and minimum values from the site, where the PV system will be deployed. As a consequence, all the formulas of the mathematical models used will also be updated. In addition, depending on one of the desired properties of the system, as autonomy of the batteries, the offer of the energy, or even the power supply from the system to check, whether it is not accomplished (said satisfied), ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the property violation (system fail) happened. 

>>>>

The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. 
In Step 1, the PV input data (e.g., load power demand and load energy consumption) and the formulas to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In Step 2, the sizing check of the PV system takes place to make sure that the components meet international requirements \textcolor{red}{cite here those requirements} toward a well designed PV project.

@@

In Step 3, weather variables (e.g., solar irradiance and ambient temperature) will be systematically explored by our verification engine based on maximum and minimum values from the site, where the PV system will be deployed. As a consequence, all the formulas of the employed mathematical models will also be updated. In addition, depending on one of the desired properties of the system, as autonomy of the batteries, the offer of the energy, or even the power supply from the system to check, whether it is not accomplished (said satisfied), ESBMC accuses a failure, and the diagnostic counterexample shows in which condition the property violation (system fail) happened. 
